### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Grammar edits of Estimation Strategy

The model is a discrete time, non-proportional, competing risk hazard model with two exit 
states: either a boy or a girl is born.
The unit of analysis is a spell, the period from one birth to the next.
For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
the spell continues until time $t_i$, when either a birth occurs or the spell 
is censored.%
\footnote{
The time of censoring is assumed independent of the hazard rate,
as is standard in the literature.
}
There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
$J_i$ is a random variable indicating which event took place.
The discrete time hazard rate $h_{ijt}$ is specified as
\begin{equation}
 h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
 {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
 \label{eq:hazard}
\end{equation}
where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
individual, household, and community characteristics discussed below,
and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
by dummies and the associated coefficients,
\begin{equation}
D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
\end{equation}
with $D_m = 1$ if $t=m$ and zero otherwise.
This approach to modeling the baseline hazard is flexible and does not place 
overly strong restrictions on the baseline hazard.

The explanatory variables in $\mathbf{Z}$ and the interactions between them 
are the non-proportional part of the model, which means that they are
interacted with the baseline hazard:
\begin{equation}
 \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
\end{equation}
where $D_j(t)$ is the piece-wise linear baseline hazard and $\mathbf{Z}_1$ captures sex 
composition of previous children, if any, and $Z_2$ captures area of residence.
The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
but to further minimize any potential bias from assuming proportionality, estimations 
are done separately for different levels of mothers' education and for different 
time periods.%
\footnote{
The choice of which variables to use for non-proportionality is discussed in more detail
in the ``Explanatory Variables'' section.
}

>>>>

The model is a discrete time, non-proportional, competing risk hazard model with two exit 
states: either a boy or a girl is born.
The unit of analysis is a spell, the period from one birth to the next.
For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
the spell continues until time $t_i$, when either a birth occurs or the spell 
is censored.%
\footnote{
The time of censoring is assumed independent of the hazard rate,
as is standard in the literature.
}
There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
$J_i$ is a random variable indicating which event took place.
The discrete time hazard rate $h_{ijt}$ is 
\begin{equation}
 h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
 {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
 \label{eq:hazard}
\end{equation}
where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
individual, household, and community characteristics discussed below,
and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
by dummies and the associated coefficients,
\begin{equation}
D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
\end{equation}
with $D_m = 1$ if $t=m$ and zero otherwise.
This approach to modeling the baseline hazard is flexible and does not place 
overly strong restrictions on the baseline hazard.

The explanatory variables in $\mathbf{Z}$ and the interactions between them 
are the non-proportional part of the model, which means that they are
interacted with the baseline hazard:
\begin{equation}
 \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
\end{equation}
where $D_j(t)$ is the piece-wise linear baseline hazard and $\mathbf{Z}_1$ captures sex 
composition of previous children, if any, and $Z_2$ captures area of residence.
The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
but to further minimize any potential bias from assuming proportionality, estimations 
are done separately for different levels of mothers' education and different 
periods.%
\footnote{
I discuss the choice of which variables to use for non-proportionality in more detail
in the ``Explanatory Variables'' section.
}
